# License (BSD 2-Clause)

# Copyright (C) 2021 University of Dundee. All Rights Reserved.

# Redistribution and use in source and binary forms, with or without modification, are 
# permitted provided that the following conditions are met:

#  Redistributions of source code must retain the above copyright notice, this list of
#  conditions and the following disclaimer. Redistributions in binary form must reproduce
#  the above copyright notice, this list of conditions and the following disclaimer in
#  the documentation and/or other materials provided with the distribution.
#  THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS \"AS IS\" AND
#  ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT LIMITED TO, THE IMPLIED WARRANTIES
#  OF MERCHANTABILITY AND FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT
#  SHALL THE COPYRIGHT OWNER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL,
#  SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT LIMITED TO, PROCUREMENT OF
#  SUBSTITUTE GOODS OR SERVICES; LOSS OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION)
#  HOWEVER CAUSED AND ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR
#  TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE OF THIS
#  SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE."

## Loading libraries

```{r load_libraries}
library(magrittr)
library(ggplot2)
library(romero.gateway)
```

## Log in to the IDR
```{r connect}
server <- OMEROServer(host = 'wss://idr.openmicroscopy.org/omero-ws', port = 443L, username='public', password='public')
server <- connect(server)
paste('Successfully logged in as', server@user$getUserName())
```

## Find the attachments
```{r find_attachments}
screenId <- 2751
fileLibrary <- "screenA-library.csv"
fileProcessed <- "screenA-processed.csv"
omeScreen <- loadObject(server, 'ScreenData', screenId)
fileLibraryAnnotation <- getAnnotations(server, 'ScreenData', getOMEROID(omeScreen), nameFilter = fileLibrary)
fileProcessedAnnotation <- getAnnotations(server, 'ScreenData', getOMEROID(omeScreen), nameFilter = fileProcessed)
annotationFileLibraryID = as.integer(fileLibraryAnnotation$FileID)
annotationFileLibraryID <- annotationFileLibraryID[[length(annotationFileLibraryID)]]
annotationFileProcessedID = as.integer(fileProcessedAnnotation$FileID)
annotationFileProcessedID <- annotationFileProcessedID[[length(annotationFileProcessedID)]]
```

## Load the results associated to the plate
This is the first plate. If you select a new plate, change the ID below and the number in 
the file name e.g. for the second plate, id is 7651 and the name will be 'single_cell_features_raw_002.csv'.

```{r set_parameters}
plateId <- 7737
plateNumber <- "001"
fileRawSingleCell <- paste("single_cell_features_raw_", plateNumber, ".csv", sep="")
fileProcessedSingleCell <- paste("single_cell_features_processed_", plateNumber, ".csv", sep="")
```

```{r load_plate_results}
omePlate <- loadObject(server, 'PlateData', plateId)
fileRawSingleCellAnnotation <- getAnnotations(server, 'PlateData', getOMEROID(omePlate), nameFilter = fileRawSingleCell)
fileProcessedSingleCellAnnotation <- getAnnotations(server, 'PlateData', getOMEROID(omePlate), nameFilter = fileProcessedSingleCell)
annotationFileRawSingleCellID = as.integer(fileRawSingleCellAnnotation$FileID)
annotationFileRawSingleCellID <- annotationFileRawSingleCellID[[length(annotationFileRawSingleCellID)]]
annotationFileProcessedSingleCellID = as.integer(fileProcessedSingleCellAnnotation$FileID)
annotationFileProcessedSingleCellID <- annotationFileProcessedSingleCellID[[length(annotationFileProcessedSingleCellID)]]
```
## Load the annotations as R-Dataframes
```{r load_csv}
lib <- loadCSV(server, annotationFileLibraryID)
well_summaries <- loadCSV(server, annotationFileProcessedID)
raw_single_cell <- loadCSV(server, annotationFileRawSingleCellID)
processed_single_cell <- loadCSV(server, annotationFileProcessedSingleCellID)
```
## Close the connection
```{r close_connection}
disconnect(server)
```
## Show distributions of phenotypes
Example to show joining of library and summaries files to plot distributions of a quantitative phenotype.
```{r show_phenotypes}
lib %>%
  dplyr::left_join(well_summaries,by=c("Plate","Well")) %>%
  dplyr::select(residuals_mean_EU_model,phenotype_mean_EU_model,`Gene.Symbol`) %>%
  dplyr::mutate(negative_control = `Gene.Symbol`=="Scrambled") %>%
  dplyr::filter(!is.na(`Gene.Symbol`)) %>%
  ggplot(aes(x=residuals_mean_EU_model,fill=as.factor(phenotype_mean_EU_model))) + 
  geom_histogram(bins = 100) + 
  facet_grid(negative_control~.,labeller = "label_both") +
  scale_fill_discrete("Mean EU phenotype") +
  theme_minimal()
```
## Show top hits
Example to show joining of library and summaries files to list all mean-EU 
hits on the selected plate.

```{r show_hits}
lib %>%
  dplyr::left_join(well_summaries,by=c("Plate","Well")) %>%
  dplyr::filter(phenotype_mean_EU_model != 0) %>%
  dplyr::filter(Plate==plateNumber) %>%
  dplyr::select(`Gene.Symbol`,residuals_mean_EU_model,phenotype_mean_EU_model) %>%
  dplyr::arrange(dplyr::desc(residuals_mean_EU_model)) 
```
## Compare raw and processed
Example to show comparison of raw and processed feature values. Note that offset arises from background correction (subtraction of a constant value) and slope change arises from plate-to-plate correction (plate-wise multiplication to equalise scrambled medians).

``{r compare_raw_processed}
processed_single_cell %>%
  dplyr::filter(Well=="G06") %>%
  dplyr::inner_join(raw_single_cell,by=c("Object_ID","Plate","Well","well_pos_y","well_pos_x"),suffix=c("_processed","_raw")) %>%
  ggplot(aes(x=Nuclei_Intensity_Mean_EU_raw,Nuclei_Intensity_Mean_EU_processed)) +
  geom_point() +
  geom_abline() +
  theme_minimal() +
  expand_limits(x=0,y=0)
```
## Single cell data with library info
Example to show joining of library, summaries and processed single cell data to plot the single cell EU measurements as a function of protein content and cell cycle stage, for all mean-EU ‘hits’ on the selected plate.
```{r extract_subset}
processed_single_cell <- processed_single_cell[sample(1:nrow(processed_single_cell), 150000, replace=FALSE),]
```

```{r compare_with_lib}
processed_single_cell %>%
  dplyr::filter(Plate==plateNumber) %>%
  dplyr::left_join(well_summaries,by=c("Plate","Well")) %>%
  dplyr::left_join(lib,by = c("Plate", "Well")) %>% {
    ggplot() +
      geom_point(data=dplyr::filter(.,`Gene Symbol`=="Scrambled") %>% 
                   dplyr::select(Cell_Intensity_Sum_SE,
                                 Nuclei_Intensity_Sum_EU),
                 mapping=aes(x=Cell_Intensity_Sum_SE,
                             y=Nuclei_Intensity_Sum_EU), color="grey80", size=0.1) +
      geom_point(data=dplyr::filter(.,phenotype_mean_EU_model!=0 & `Gene Symbol` !="KIF11" ) %>% 
                   dplyr::select(phenotype_mean_EU_model,
                                 Cell_Intensity_Sum_SE,
                                 Nuclei_Intensity_Sum_EU,
                                 Cell_Cycle_Stage,
                                 `Gene Symbol`,
                                 Well) %>%
                   dplyr::mutate(well_id = paste(`Gene Symbol`,"(",Well,")")) %>%
                   dplyr::distinct(),
                 mapping=aes(x=Cell_Intensity_Sum_SE,
                             y=Nuclei_Intensity_Sum_EU,
                             col=Cell_Cycle_Stage), size=0.1) +
      geom_text(data=dplyr::filter(.,phenotype_mean_EU_model!=0 & `Gene Symbol` !="KIF11" ) %>% 
                  dplyr::select(phenotype_mean_EU_model,
                                n_cells,
                                `Gene Symbol`,
                                Well) %>%
                  dplyr::mutate(well_id = paste(`Gene Symbol`,"(",Well,")")) %>%
                  dplyr::distinct(),
                mapping=aes(x=-Inf,y=Inf,label=paste("#cells =",n_cells)),
                hjust=-0.1,vjust=1,size=8/.pt,fontface="plain",family="sans") +
      facet_wrap(phenotype_mean_EU_model~well_id,labeller = "label_both",ncol=3) +
      theme_minimal(base_size = 8) +
      ggtitle(paste("Plate", plateNumber, sep=" "))
```



